Millions of Type Errors

### 2023-09-08 programming23/paper.tex
type error survival table: add keep drop

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}

@@

=== BEN START HERE

@@

TODO which type errors at end of session?

\begin{figure}[t]
  Below, edit range only.
  Each record with an edit range error adds +1 to at least 1 row.

  \smallskip

  %% TODO draw bars or curves b/c numbers are too hard to compare horizontally
  \begin{tabular}{lrrr}
    Error Label & \# Add & \# Keep & \# Remove \\\midrule
    CodeTooComplex
    & 0 & 0 & 0 \\
    UnificationTooComplex
    & 0 & 0 & 0 \\[1ex]
    SyntaxError
    & 30 & 0 & 76 \\
    UnknownSymbol
    & 12 & 14 & 19 \\
    UnknownProperty
    & 3 & 1 & 4 \\
    UnknownRequire
    & 1 & 5 & 0 \\
    GenericError
    & 1 & 0 & 1 \\
    CountMismatch
    &  1 &  0 &  1 \\
    OptionalValueAccess
    &  0 &  0 &  1 \\
  \end{tabular}

  \caption{Errors overview}
  \label{f:errors-overview}
\end{figure}

@@

\begin{figure}[t]

  %% TODO import code from tmp to nsa
  {Few local adds => Few people ignoring script analysis}
  \smallskip

  \begin{tabular}{lrrrr}
    & Local Remove & Local Add & Nonlocal Remove & Nonlocal Add \\
    Mode
    & \#err (\#log)
    & \#err (\#log)
    & \#err (\#log)
    & \#err (\#log) \\\midrule
    \mnocheck{}   & 86 (71) & 0 (0) & 110 (57) & 161 (74) \\
    \mnonstrict{} & 87 (25) & 9 (3) & 185 (29) & 207 (37) \\
    \mstrict{}    &  1  (1) & 0 (0) &  14  (6) &   6  (3) \\
  \end{tabular}

  \caption{Per-mode comparison}
  \label{f:mode-errors}
\end{figure}

>>>>

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}

@@

@@

NOTE can't ask about type errors at end because we don't know
the end.
The final record can be sent minutes before the end of session.

\begin{table}[t]

    \begin{tabular}{lr@{~}r@{~}rr@{~}r@{~}rr@{~}r@{~}r}
      & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
      & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} \\\midrule
      TypeMismatch & {0} & {0} & {0} & {159} & {62} & {129} & {21} & {10} & {28} \\
      UnknownSymbol & {0} & {0} & {0} & {2348} & {496} & {2973} & {49} & {19} & {55} \\
      UnknownProperty & {0} & {0} & {0} & {347} & {180} & {385} & {19} & {19} & {35} \\
      NotATable & {0} & {0} & {0} & {7} & {2} & {8} & {2} & {0} & {1} \\
      CannotExtendTable & {0} & {0} & {0} & {7} & {9} & {10} & {0} & {0} & {1} \\
      OnlyTablesCanHaveMethods & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      DuplicateTypeDefinition & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
      CountMismatch & {0} & {0} & {0} & {223} & {48} & {269} & {12} & {2} & {17} \\
      FunctionDoesNotTakeSelf & {0} & {0} & {0} & {4} & {6} & {5} & {0} & {0} & {0} \\
      OccursCheckFailed & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
      UnknownRequire & {0} & {0} & {0} & {91} & {39} & {85} & {12} & {3} & {4} \\
      IncorrectGenericParameterCount & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
      SyntaxError & {8349} & {314} & {19220} & {983} & {46} & {2658} & {16} & {0} & {71} \\
      UnknownPropButFoundLikeProp & {0} & {0} & {0} & {26} & {18} & {21} & {1} & {0} & {1} \\
      GenericError & {0} & {0} & {0} & {206} & {52} & {203} & {8} & {1} & {9} \\
      CannotCallNonFunction & {0} & {0} & {0} & {17} & {4} & {20} & {1} & {0} & {1} \\
      ExtraInformation & {0} & {0} & {0} & {48} & {7} & {39} & {2} & {0} & {1} \\
      ModuleHasCyclicDependency & {0} & {0} & {0} & {20} & {9} & {15} & {0} & {0} & {1} \\
      IllegalRequire & {0} & {0} & {0} & {16} & {3} & {33} & {0} & {0} & {2} \\
      FunctionExitsWithoutReturning & {0} & {0} & {0} & {9} & {3} & {6} & {11} & {5} & {8} \\
      CannotInferBinaryOperation & {0} & {0} & {0} & {1} & {2} & {1} & {7} & {6} & {9} \\
      MissingProperties & {0} & {0} & {0} & {11} & {3} & {11} & {6} & {4} & {6} \\
      OptionalValueAccess & {0} & {0} & {0} & {40} & {52} & {27} & {6} & {2} & {7} \\
      MissingUnionProperty & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      TypesAreUnrelated & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {1} \\
    \end{tabular}

  \caption{Type error survival}
  \label{t:type-error-survival}
\end{table}

@@
